Retrofitting Effect Handlers onto OCaml

### 2021-03-12 retro-concurrency.tex
updates

\documentclass[sigplan,screen]{acmart}
\setcopyright{none}
\acmPrice{}
\acmDOI{10.1145/3453483.3454039}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{pldi21main-p82-p}
\acmISBN{978-1-4503-8391-2/21/06}
\acmConference[PLDI '21]{Proceedings of the 42nd ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 20--25, 2021}{Virtual, UK}
\acmBooktitle{Proceedings of the 42nd ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '21), June 20--25, 2021, Virtual, UK}

@@

\author{KC Sivaramakrishnan}
\affiliation{
  \institution{IIT Madras}            %% \institution is required
	\city{Chennai}
	\country{India}
}
\email{kcsrk@cse.iitm.ac.in}          %% \email is recommended

\author{Stephen Dolan}
\affiliation{
  \institution{OCaml Labs}            %% \institution is required
	\city{Cambridge}
	\country{UK}
}
\email{stephen.dolan@cl.cam.ac.uk}

\author{Leo White}
\affiliation{
  \institution{Jane Street}            %% \institution is required
	\city{London}
	\country{UK}
}
\email{leo@lpw25.net}

\author{Sadiq Jaffer}
\affiliation{
  \institution{Opsian and OCaml Labs} %% \institution is required
	\city{Cambridge}
	\country{UK}
}
\email{sadiq@toao.com}

\author{Tom Kelly}
\affiliation{
  \institution{OCaml Labs}            %% \institution is required
	\city{Cambridge}
	\country{UK}
}
\email{tom.kelly@cantab.net}

\author{Anil Madhavapeddy}
\affiliation{
  \institution{University of Cambridge Computer Laboratory and OCaml Labs}            %% \institution is required
	\city{Cambridge}
	\country{UK}
}
\email{avsm2@cl.cam.ac.uk}          %% \email is recommended

@@

>>>>

\documentclass[sigplan,screen]{acmart}
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3453483.3454039}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{pldi21main-p82-p}
\acmISBN{978-1-4503-8391-2/21/06}
\acmConference[PLDI '21]{Proceedings of the 42nd ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 20--25, 2021}{Virtual, UK}
\acmBooktitle{Proceedings of the 42nd ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '21), June 20--25, 2021, Virtual, UK}

@@

\author{KC Sivaramakrishnan}
\affiliation{
  \institution{\small IIT Madras}            %% \institution is required
	\city{\small Chennai}
	\country{\small India}
}
\email{kcsrk@cse.iitm.ac.in}          %% \email is recommended

\author{Stephen Dolan}
\affiliation{
  \institution{\small OCaml Labs}            %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{stephen.dolan@cl.cam.ac.uk}

\author{Leo White}
\affiliation{
  \institution{\small Jane Street}            %% \institution is required
	\city{\small London}
	\country{\small UK}
}
\email{leo@lpw25.net}

\author{Sadiq Jaffer}
\affiliation{
  \institution{\small Opsian and OCaml Labs} %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{sadiq@toao.com}

\author{Tom Kelly}
\affiliation{
  \institution{\small OCaml Labs}            %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{tom.kelly@cantab.net}

\author{Anil Madhavapeddy}
\affiliation{
  \institution{\small University of Cambridge Computer Laboratory and OCaml Labs}            %% \institution is required
	\city{\small Cambridge}
	\country{\small UK}
}
\email{avsm2@cl.cam.ac.uk}          %% \email is recommended

@@

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011041.10011048</concept_id>
       <concept_desc>Software and its engineering~Runtime environments</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011024.10011034</concept_id>
       <concept_desc>Software and its engineering~Concurrent programming structures</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011024.10011027</concept_id>
       <concept_desc>Software and its engineering~Control structures</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011009.10010175</concept_id>
       <concept_desc>Software and its engineering~Parallel programming languages</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011009.10011014</concept_id>
       <concept_desc>Software and its engineering~Concurrent programming languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Runtime environments}
\ccsdesc[500]{Software and its engineering~Concurrent programming structures}
\ccsdesc[500]{Software and its engineering~Control structures}
\ccsdesc[300]{Software and its engineering~Parallel programming languages}
\ccsdesc[500]{Software and its engineering~Concurrent programming languages}

\keywords{Effect handlers, Backwards compatibility, Fibers, Continuations,
Backtraces}
